Fixing Translation Divergences in Parallel Corpora for Neural MT

### 2018-07-26 EMNLP/divergence.tex

We {\bf (R)}eplace random sequences of words by a sequence of words with same part-of-speeches. 
The rationale behind this method is to keep the new sentences as grammatical as possible. 
%Otherwise the network can learn to detect non-grammatical sentences to predict divergence.
Words that are not replaced are considered parallel ($-1$) while those replaced are assigned the divergent label ($+1$). 
Words aligned to any replaced word are also assigned the divergent label ($+1$). For instance, given the original sentence pair:

@@

In addition to the basic tokenisation detailed in Section~\ref{divergence} we perform Byte-Pair Encoding~\cite{Sennrich2016} with $30,000$ merge operations learned from both English and French data.
Neural MT systems are based on the open-source project \texttt{OpenNMT}\footnote{http://opennmt.net}. We use a bidirectional RNN encoder with $4$ LSTM layers with each containing $1,000$ cells. 
Word embeddings have a size of $300$ cells. We set the dropout probability to $0.3$. Batch size is set to $64$. The maximum length of both source and target sentences is set to $80$. % and we limit the vocabulary size to $50K$ words for both source and target languages.
The default optimiser is SGD with the starting learning rate of $1.0$. We start to decay the learning rate from epoch $10$ or when we detect increasing perplexity as compared to the previous epoch on a validation set. We stop training after $20$ epochs.

@@

\begin{table}[h!]
\small
\center
\begin{tabular}{lccl}
\hline
\bf Data & \bf Ref (M) & \bf Fix (M) & \bf Test (BLEU) \\ %MSLT & \bf NEWS \\
\hline
\multicolumn{3}{c}{\scriptsize{OpenSubtitles English-French}} \\
\texttt{all}                  & 27.2 & - & 42.18 \\
\texttt{semb}            & 18.0 & - & 41.95\\
\texttt{wemb}           & 15.5 & - & 43.12  ($+0.94$)\\
%\texttt{wemb}           & 21.5 & - & 42.56 \\
\texttt{wemb+fix}   & 15.5 & 2.5 & \\
\texttt{wemb}           & 18.0 & - & 43.19  ($+1.01$)\\
%\texttt{wemb+fix}   & 15.5 & 5.0 & \\
\hline
\multicolumn{3}{c}{\scriptsize{Paracrawl English-German}} \\
%\texttt{all}                  & 100.0 & 12.56 \\ 
\texttt{all}                  & 22.2 & - & 19.27 \\ 
\texttt{semb}            & 15.0 & - & \\
\texttt{wemb}           & 15.0 & - & 21.52 ($+2.25$)\\
%\texttt{wemb}           & 12.5 &   \\
%\texttt{wemb+fix}   & 12.5+2.5 & \\
\hline
\end{tabular}
\caption{BLEU scores obtained by neural MT using different subsets of the OpenSubtitles and Paracrawl corpora.}
\label{results}
\end{table}

>>>>

We {\bf (R)}eplace random sequences of words by a sequence of words with same parts-of-speech. 
The rationale behind this method is to keep the new sentences as grammatical as possible. 
%Otherwise the network can learn to detect non-grammatical sentences to predict divergence.
Words that are not replaced are considered parallel ($-1$) while those replaced are assigned the divergent label ($+1$). 
Words aligned to any replaced word are also assigned the divergent label ($+1$). For instance, given the original sentence pair:

@@

In addition to the basic tokenisation detailed in Section~\ref{divergence} we perform Byte-Pair Encoding~\cite{Sennrich2016} with $30,000$ merge operations learned from both English and French data.
Neural MT systems are based on the open-source project \texttt{OpenNMT}\footnote{http://opennmt.net}. We use a Transformer model with same configuration in paper \cite{Transformer2017}, i.e, both encoder and decoder have 6 layers; Multi-head attention is performed over 8 heads. Hidden layer's size is 512. The inner layer of feedforward network is of size $2048$. Word embeddings have a size of $512$ cells. We set the dropout probability to $0.1$. Batch size is set to $3072$. The maximum length of both source and target sentences is set to $80$ and we limit the vocabulary size to $50K$ words for both source and target languages.

The optimiser is Adam avec learning rate that was introduced in paper \cite{Transformer2017} with $\beta_1 = 0.9$, $\beta_2 = 0.98$, $\eta = 10^{-9}$, $warmup\_steps = 4000$. We stop training after 30 epochs.

@@

\begin{table}[h!]
\small
\center
\begin{tabular}{lccl}
\hline
\bf Data & \bf Ref (M) & \bf Fix (M) & \bf Test (BLEU) \\ %MSLT & \bf NEWS \\
\hline
\multicolumn{3}{c}{\scriptsize{OpenSubtitles English-French}} \\
\texttt{all}                  & 27.2 & - & 42.18 \\
\texttt{semb}            & 18.0 & - & 41.95\\
\texttt{wemb}           & 15.5 & - & 43.12  ($+0.94$)\\
%\texttt{wemb}           & 21.5 & - & 42.56 \\
\texttt{wemb+fix}   & 15.5 & 2.5 & 44.19 \\
\texttt{wemb}           & 18.0 & - & 43.19  ($+1.01$)\\
%\texttt{wemb+fix}   & 15.5 & 5.0 & \\
\hline
\multicolumn{3}{c}{\scriptsize{Paracrawl English-German}} \\
%\texttt{all}                  & 100.0 & 12.56 \\ 
\texttt{all}                  & 22.2 & - & 19.27 \\ 
\texttt{semb}            & 15.0 & - & 20.23\\
\texttt{wemb}           & 15.0 & - & 21.52 ($+2.25$)\\
\texttt{wemb}           & 17.5 & - & 21.97   \\
\texttt{wemb+fix}   & 15 & 2.5 & 22.42\\
\hline
\end{tabular}
\caption{BLEU scores obtained by neural MT using different subsets of the OpenSubtitles and Paracrawl corpora.}
\label{results}
\end{table}
